---
title: 'Rider Membership Data: Portraying the disparity in the number of registered
  riders across categories amidst an escalated registration fee.'
author: "Sharon Ogwu"
date: "15th April 2024"
output: 
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(here)
library(skimr)
library(janitor)
library(readr)
library(lubridate)
library(ggplot2)
library(scales)
knitr::opts_chunk$set(echo = TRUE)
```

### This analysis was conducted for a rider company to determine if the volume of registered riders in their specific categories, particularly annual members, has decreased due to an increased registration fee in the preceding year


```{r data}


Raw_data<-read_csv("R sample.csv")
#Cleaning the data
Raw_data$ride_lengths<-hms(Raw_data$Ride_Length)
R_data<-clean_names(Raw_data)

#Analyzing the data
R<- R_data%>%
  select(-ride_length)%>%
  group_by(member_casual)%>%
  arrange(-ride_lengths)

#Counting the riders based on category
table(R_data$member_casual)
```

**This chart illustrates the fluctuation in registered riders across categories. Despite the higher membership fee for annual members compared to casual riders, there was growth in both categories over the past year, indicating that the fee increment did not adversely impact registration.


```{r pressure, echo=FALSE}

      
summary_datas <- data.frame(
  member_casual = c("member", "casual"),
  count = c(378.407, 48.480)  
)
# Converting the count to percentage
total_counts <- sum(summary_datas$count)
summary_datas$percentage <- (summary_datas$count / total_counts) * 100

# Creating the chart
ggplot(data = summary_datas) +
  geom_bar(mapping = aes(x = member_casual, y = percentage, fill = member_casual), stat = "identity") +
  labs(title = "Rider Membership Data", subtitle = "variation in the number of registered riders based on category") +ylab("count of riders by category")+
  theme(plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  scale_y_continuous(
    limits = c(0, 100),  
    labels = percent_format(accuracy = 1, scale = 1/1),
    breaks = seq(0, 100, 10)  
  )
```

